---
title: "My First Document"
author: "David Piekarski"
date: "11/30/2018"
output:
  word_document: default
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#CheatSheet
Number of hashtages representes the level of teh ehader, thus, fewer hashtags means larger font

#Level One Header
## R Markdown
###Level Three Header


##Links
Here is a link to [Google](http://www.google.com): Names in square brackets followed by link in parentheses.
You can also include the raw link by putting it between "<>" resulting in, <http://www.google.com>

##Emphasis
*Italics* are created by bookending a word in asterisks while **Bolds** are created by bookending a word in double asterisks.  Alternately, you can use _single_ or __double underscores__ 




If you want to show r code, without running it, put code between three backticks
```
2 + 2 =4
ggplot(data, aes(x=x, y=y)) + geom_point()
```

__Non numbered list__: each indent must be four spaces for markdown to recognize that it is a list

* Breakfast
    - food
        + eggs
        + rice
        + toast


####Format Quotes
> this is a block quote, started with a greater than symbol
>
> > you can also nest a blockquote
> if you add five spaces after greater than, you can nest code 

>     2 + 2
####The below text is actual r code  that has been run
```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:
##
```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
